---
title: "Activity street"
author: "Hongji Jiang"
output:
  html_notebook:
    fig_height: 3
    fig_width: 5
data: 4/14/2020
---


```{r}
library(ggplot2)
library(DataComputing)
library(dplyr)
library(readr)

download.file(url="http://tiny.cc/dcf/CMS_ProvidersSimple.rds",
              destfile = "YourNameForTheFile.rds")
DataTable <- readRDS("YourNameForTheFile.rds")
```
##Example: extract the PO Box number from an address
```{r}
Addresses <- read_csv("http://tiny.cc/dcf/street-addresses.csv")
Sample <- 
  Addresses %>%
  sample_n(size = 50)

Matches <- 
  Sample %>%
  filter(grepl(pattern = "PO", address))

Dont <- 
  Sample %>%
  filter( ! grepl(pattern = "PO", address))

pattern <- "BOX\\s+(\\d+)"

Matches <- 
  Sample %>% 
  filter(grepl(pattern, address))

Dont <-
  Sample %>%
  filter( ! grepl(pattern, address))
Dont

BoxNumbers <- 
  Sample %>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)
BoxNumbers

```

##explain each line of code in English (either narrative or commented code)
```{r}
pattern <- "(ST|RD|ROAD)"
##Assign "(ST|RD|ROAD)" to pattern

LeftOvers <-
  Addresses %>% 
  filter( ! grepl(pattern, address),
          ! grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          ! grepl(" BOX ", address)
          )
##Filter out any variable in address that contain any st, rd, or road.
##Filter out any address that contain " APT" or "UNIT [digit]" zero or more times in the end
##Filter out any address that contain " BOX "
View(LeftOvers)
```

##expand to match several more patterns (at least 12 total)
```{r}
pattern1 <- "CIRCLE$|CIR$"
pattern2 <- "WAY$"
pattern3 <- "AVE$"
pattern4 <- "LN$"
pattern5 <- "DR$"
pattern6 <- "TRAIL$"
pattern7 <- "BX"
pattern8 <- "HOUSE|HOME|HALL"
pattern9 <- "DRIVE$"
pattern10 <- "COLLEGE$|UNIVERSITY$"
pattern11 <- "\\d"
pattern12 <- "HOSPITAL$"


LeftOvers %>% 
  filter( ! grepl(pattern1, address),
          ! grepl(pattern2, address),
          ! grepl(pattern3, address),
          ! grepl(pattern4, address),
          ! grepl(pattern5, address),
          ! grepl(pattern6, address),
          ! grepl(pattern7, address),
          ! grepl(pattern8, address),
          ! grepl(pattern9, address),
          ! grepl(pattern10, address),
          ! grepl(pattern11, address),
          ! grepl(pattern12, address)
          )

```

##provide a table in descending order of popularity for the street name identifiers you found
```{r}
pattern1. <- LeftOvers%>%
  filter(grepl(pattern1,address))%>%
  mutate( pattern = "CIRCLE$|CIR$")
pattern2. <- LeftOvers%>%
  filter(grepl(pattern1,address))%>%
  mutate( pattern = "WAY$")
pattern3. <- LeftOvers%>%
  filter(grepl(pattern3,address))%>%
  mutate( pattern = "AVE$")
pattern4. <- LeftOvers%>%
  filter(grepl(pattern4,address))%>%
  mutate( pattern = "LN$")
pattern5. <- LeftOvers%>%
  filter(grepl(pattern5,address))%>%
  mutate( pattern = "DR$")
pattern6. <- LeftOvers%>%
  filter(grepl(pattern6,address))%>%
  mutate( pattern = "TRAIL$")
pattern7. <- LeftOvers%>%
  filter(grepl(pattern7,address))%>%
  mutate( pattern = "BX")
pattern8. <- LeftOvers%>%
  filter(grepl(pattern8,address))%>%
  mutate( pattern = "HOUSE|HOME|HALL")
pattern9. <- LeftOvers%>%
  filter(grepl(pattern9,address))%>%
  mutate( pattern = "DRIVE$")
pattern10. <- LeftOvers%>%
  filter(grepl(pattern10,address))%>%
  mutate( pattern = "COLLEGE$|UNIVERSITY$")
pattern12.<- LeftOvers%>%
  filter(grepl(pattern12,address))%>%
  mutate( pattern = "HOSPITAL$")


patternplot <- pattern1.%>%
  full_join(pattern2., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern3., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern4., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern5., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern6., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern7., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern8., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern9., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern10., by = c("address" ="address", "pattern" = "pattern"))%>%
  full_join(pattern12., by = c("address" ="address", "pattern" = "pattern"))%>%
  group_by(pattern)%>%
  summarise(count = n())%>%
  arrange(desc(count))
patternplot
```

##use ggplot to construct a bar chart in descending order of popularity for the street name identifiers you found.
```{r}
ggplot(patternplot,aes(x = pattern, y = count)) + geom_bar(stat = "identity") + coord_flip()

```





