---
title: "DC Exercise 15"
author: "Hongji Jiang"
output:
  html_notebook:
    fig_height: 3
    fig_width: 5
data: 4/7/2020
---

#15.1
```{r}
library(ggplot2)
library(DataComputing)
library(dplyr)
```

```{r}
mosaicData::CPS85

CPS85%>% 
  ggplot(aes(y = wage, x = sex )) + 
  geom_boxplot(aes(fill = sex)) + ylab("wage") + xlab( "sex") +  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

#15.2
1 most likely the height would be 165cm
2 woman most likely at 161 cm, man most likely at 176 cm
3 the most likely bmi for 40 years old should be within 25-28, and for 70 years old is within 25-30

#15.3
```{r}

CPS85 %>% 
  ggplot(aes(x = educ, y = wage, color = sex)) + stat_smooth(method = lm) + geom_point() + theme(legend.position = "top") + ylim(-1,16)

```

#15.4
```{r}
mosaicData::Galton
Galton%>%ggplot(aes(x = height, y= mother))+facet_wrap(~sex, ncol = 2)+geom_density_2d()
```

#15.5
Part 1
1:no, we can't find a specific trend of the relationship of high elderly populations and high child populations from the graph

2:no, the confidence interval does not fit the data very well.

Part2
1:The plat line is kind of fit the data since they both have a trend of decrease as x axis increase
2:The confidence interval at 20 zipcode is about 10, and is about 8 when 80 zipcode. The ratio is about 4/5.
3:Yes, since confidence band become narrower as there are more points.













