---
title: "DC Exercise 18"
author: "Hongji Jiang"
output:
  html_notebook:
    fig_height: 3
    fig_width: 5
data: 4/26/2020
---




<br>
<br>
<br>
<br>

##18.1
<br>

###1

house price<br>
living area<br>
bathroom number<br>
fireplace<br>
bedroom<br>

###2
No, since there are no branches after living area less than 1080 squarefeet
<br>

###3
```{r}
179796.647-151424.497
```
The typical difference is 28372.15
<br>

###4
When living area is greater than 2816 square feet, the fireplace that is less or equal to one and greater to one will make difference
<br>
<br>
<br>
<br>

##18.2
```{r}
library(partykit)
library(party)
library(dplyr)
library(ggplot2)
library(DataComputing)
DataComputing::NCHS 
```

###1
```{r}
CompleteCases <- 
  NCHS %>%
  select(diabetic, weight, age, bmi, chol, smoker) %>%
  na.omit() 
CompleteCases %>% nrow()



mod2 <- party::ctree(diabetic ~ age + bmi, data = CompleteCases)

CompleteCases %>%
  mutate(probability = as.numeric(predict(mod2)), 
         likelihood = ifelse(diabetic, probability, 1-probability)) %>%
  summarise(log_likelihood = sum(log(likelihood)))

```
<br>

###2
```{r}

plot(mod2,type = "simple")

```
<br>

###3
The highest risk of biabetes is node27. The age that is higher than 60 years old with bmi greater than 35.349 would have 36.8% of chance getting disease or injured
<br>

###4
The lowest risk of diabetes is node5. The bmi under 23 and age under 36 have least possibility of 0.2% for getting injured or disease.


