---
title: "DC exercise Chapter 12"
author: "Hongji Jiang"
output:
  html_notebook:
    fig_height: 3
    fig_width: 5
data: 3/24/2020
---

#1
1
```{r}
library(ggplot2)
library(tidyverse)
library(DataComputing)
library(dplyr)
data("BabyNames")
BothSexes <-
  BabyNames %>%
  spread( key=sex, value=count ) %>%
  filter( F>1, M>1 )
BothSexes
View(BabyNames)
```

2
```{r}
BothSexes%>%
  group_by(name)%>%
  summarise(F = sum(F),M = sum(M))%>%
  mutate(ratio = abs(log(F/M)))%>%
  arrange(ratio)
```


3
```{r}
BothSexes%>%
  group_by(name)%>%
  summarise(F = sum(F),M = sum(M))%>%
  filter(M > 100, F > 100)%>%
  mutate(ratio = abs(log(F/M)))%>%
  arrange(ratio)


```

4
```{r}
BothSexes%>%
  filter(year >= 2000)%>%
  group_by(name)%>%
  summarise(F = sum(F),M = sum(M))%>%
  filter(M > 100, F > 100)%>%
  mutate(ratio = abs(log(F/M)))%>%
  arrange(ratio)

```

5
```{r}
BothSexes%>%
  group_by(name)%>%
  mutate(ratio = abs(log(F/M)))

```

#2
1
There are n male or female babies born in certain year with the name
There are number of male and number of female baby with certain name born in this year
Baby name with male or female have these number of born in 1912 and 2012

2
BP_narrow%>%
   spread(key = sex, value = nbabies)
Version two is wider since sex has been split to m and f from version one.

3
BP_wide %>%
  gather(key = year, value = nbabies, 1912, 2012 )
Version three is wider since 1912 and 2012 can be combined in version one which is narrower

4
Version two is better, because when mutate the ratio of female and male, F and M have to be in same row. And the result will show each name and year in version two

5
We should convert version one to two as we need to put M and F in same row, and also there are no need to change year from column to row since column is better for comparison



#3
1
A is wider since the country is spreaded
B is wider since year is spreaded
C Can not tell cause each spread one variable

2
Table two, by compare the data in each row, we can find the difference between years

3
Table three since we can directly add the continent column and spread only the continent variable. Therefore, the answer would be the data for each continent.



#4
1
The subject has also been gathered, there are no need to gather subject since subject fit to each cases.

2
BP_wide %>%
  gather(key = when, value = sbp, before, after)
































